The impact of cosmic variance on simulating weak lensing surveys

### 2015-02-26 Writeup/reply.tex
more editing

We thank the referee for carefully reading our manuscript and for the acknowledgment that our work is of interest
and suitable for MNRAS. We are grateful for the pointers for improving the presentation and
explanation of our work. 
Below we address the specific issues raised.

@@

\begin{shaded}
The number of galaxies in OD or UD bins is often quite different (factor of 2-4?). It would be useful to comment on whether this difference can account for some of the differences in mean quantities plotted. I think the effect due to differences in the number of galaxies should be small for rms(e), but a specific comment on the relative effect would be useful. A straightforward way to verify this is to repeat the calculation on a selection of the same number of galaxies from both populations.
\end{shaded}
\noindent 
We guess the referee got the factor of 4 from Table 1. We would like to point out that the number of galaxies in overdense bins is higher by roughly a factor of 2 in all the plots we have made. Table 1 is now updated to reflect this clearly and considers $z=0.65-0.7$ and $z=0.7-0.75$ as two separate overdense bins.

We performed the analysis again, with a random subset containing 50 per cent of the galaxies in overdense regions, keeping the underdense bins intact. The uncertainities in the overdense bins increase due to smaller sample size. However, the difference is not significant enough to atler our conclusions. We have included this in the text as well.

>>>>

We thank the referee for carefully reading our manuscript and for the acknowledgment that our work is of interest
and suitable for MNRAS. We are grateful for the pointers for improving the presentation and
explanation of our work. 
Below we address the specific issues raised, and note that you can find all new or edited text in
the paper in red.

@@

\begin{shaded}
The number of galaxies in OD or UD bins is often quite different (factor of 2-4?). It would be useful to comment on whether this difference can account for some of the differences in mean quantities plotted. I think the effect due to differences in the number of galaxies should be small for rms(e), but a specific comment on the relative effect would be useful. A straightforward way to verify this is to repeat the calculation on a selection of the same number of galaxies from both populations.
\end{shaded}
\noindent 
The number of
galaxies in overdense bins is higher by roughly a factor of 2 in all the plots we have made. Table 1
is now updated to reflect that we plot $z=0.65-0.7$ and $z=0.7-0.75$ as two separate overdense bins.
(The previous version, which combined them, erroneously implied the factor of 4 mentioned in the
referee's comments.)

We performed the analysis again using a random subset of 50 per cent of the galaxies in overdense
regions, keeping the underdense bins intact. The uncertainities in the overdense bins increase due
to smaller sample size. However, the difference is not significant enough to alter our conclusions
based on the $p$-values from the KS and AD tests. We have noted this in Section 4.2.
